Crosslinguistic Word Orders Enable an Efficient Tradeoff between Memory and Surprisal

### 2019-09-03 writeup/control-ngrams.tex

We use Interpolated Kneser-Ney.
Hyperparameters are tuned with the same strategy as for the neural network models.

>>>>

We use a version of Kneser-Ney Smoothing.
For a sequence $w_1\dots w_k$, $N(w_{1\dots k})$ is the number of times $w_{1\dots k}$ occurs in the training set.
The unigram probabilities are estimated as
\begin{equation}
	p_1(w_t) :=   \frac{N(w_t) + \delta}{|Train| + |V| \cdot \delta}
\end{equation}
where $\delta \in \mathbb{R}_+$ is a hyperparameter.
Here $|Train|$ is the number of tokens in the training set, $|V|$ is the number of types occurring in train or held-out data.
Higher-order probabilities $p_t(w_t|w_{0 \dots t-1})$ are estimated recursively as follows.
Let $\gamma > 0$ be a hyperparameter.
If $N(w_{0 \dots t-1}) < \gamma$, set $p_t(w_t|w_{0 \dots t-1}) := p_{t-1}(w_t|w_{1\dots t-1})$.
Otherwise, we interpolate between $n$-th order and lower-order estimates:
\begin{equation}
	p_t(w_t|w_{0 \dots t-1}) :=  \frac{\operatorname{max}(N(w_{0\dots t}) - \alpha, 0.0) + \alpha \cdot \#\{w : N(w_{0 \dots t-1}w) > 0\} \cdot p_{t-1}(w_t|w_{1\dots t-1})}{N(w_{0\dots t-1})}
\end{equation}
where $\alpha \in [0,1]$ is also a hyperparameter.

Hyperparameters $\alpha, \gamma, \delta$ are tuned with the same strategy as for the neural network models.
